(Re-)bridging the anatomy ontologies with SSSOM

### 2024-06-16 presentation.tex
Add the revision number to the "about" slide.

  \begin{overlayarea}{\textwidth}{3cm}
    \only<1-2>{
      \begin{block}{Inverting a mapping}\ttfamily\scriptsize
        \textcolor<1>{red}{subject==UBERON:*} -> \textcolor<2>{red}{invert()};
      \end{block}
    }
    \only<3-4>{
      \begin{block}{Generating a simple axiom}\ttfamily\scriptsize
        \textcolor<3>{red}{predicate==skos:broadMatch} -> \textcolor<4>{red}{create\_axiom("\%subject\_id SubClassOf: \%object\_id")};
      \end{block}
    }
    \only<5-10>{
      \begin{block}{Generating a more complex axiom}\ttfamily\scriptsize
        \textcolor<5>{red}{subject==FBbt:*}\\
        \hspace{1cm} \&\& \textcolor<6>{red}{predicate==semapv:crossSpeciesExactMatch}\\
        \hspace{1cm} \&\& (\textcolor<7>{red}{mapping\_justification==semapv:ManualMappingCuration} \textcolor<8>{red}{||} \textcolor<9>{red}{confidence>=0.8)}\\
        ->  \textcolor<10>{red}{create\_axiom("\%subject\_id EquivalentTo: \%object\_id and\\
        \hspace{2cm} (BFO:0000050 some NCBITaxon:7227"))};
      \end{block}
    }
  \end{overlayarea}

@@

  \begin{block}{\includegraphics[scale=.26]{ccbysa}\hspace{.2em}2024 Damien Goutte-Gattat}
    This work is licensed under the Creative Commons Attributions-ShareAlike
    4.0 License.
  \end{block}

  \begin{block}{Contact}
    \href{mailto:dpg44@cam.ac.uk}{\texttt{dpg44@cam.ac.uk}}
  \end{block}
\end{frame}

>>>>

  \begin{overlayarea}{\textwidth}{3cm}
    \only<1-2>{
      \begin{block}{Inverting a mapping}\ttfamily\scriptsize
        \textcolor<1>{red}{subject==UBERON:*} -> \textcolor<2>{red}{invert()};
      \end{block}
    }
    \only<3-4>{
      \begin{block}{Generating a simple axiom}\ttfamily\scriptsize
        \textcolor<3>{red}{predicate==skos:broadMatch} -> \textcolor<4>{red}{create\_axiom("\%subject\_id SubClassOf: \%object\_id")};
      \end{block}
    }
    \only<5-10>{
      \begin{block}{Generating a more complex axiom}\ttfamily\scriptsize
        \textcolor<5>{red}{subject==FBbt:*}\\
        \hspace{1cm} \&\& \textcolor<6>{red}{predicate==semapv:crossSpeciesExactMatch}\\
        \hspace{1cm} \&\&
        (\textcolor<7>{red}{mapping\_justification==semapv:ManualMappingCuration}
        \textcolor<8>{red}{||} \textcolor<9>{red}{confidence>=0.8})\\
        ->  \textcolor<10>{red}{create\_axiom("\%subject\_id EquivalentTo: \%object\_id and\\
        \hspace{2cm} (BFO:0000050 some NCBITaxon:7227"))};
      \end{block}
    }
  \end{overlayarea}

@@

  \begin{block}{\includegraphics[scale=.26]{ccbysa}\hspace{.2em}%
    2024 Damien Goutte-Gattat \texttt{<dpg44@cam.ac.uk>}}
    This presentation is released under the Creative Commons
    Attributions-ShareAlike 4.0 License.
  \end{block}

  \begin{block}{Revision}\ttfamily\scriptsize
    \input{revision.tex}
  \end{block}
\end{frame}
